### 2012-06-21 inst/examples/cautious.Rmd
Cautious with lnorm noise at .2, P=1

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .5
````

@@

``` {r  SDP_Mat, dependson="grid"}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g)
````

@@

Bellman's algorithm to compute the a cautious solution that selects a fraction `P` = `r P <- 1` of the optimal harvest solution for all possible trajectories in the iterative optimization.

>>>>

``` {r miscpars, dependson="grid"}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .2
P <- 1
````

@@

``` {r  SDP_Mat, dependson="miscpars"}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g)
````

@@

Bellman's algorithm to compute the a cautious solution that selects a fraction `P` = `P` of the optimal harvest solution for all possible trajectories in the iterative optimization.
